---
title: "Data Wrangling"
author: "Franziska Nissen"
---

I had major problems with the data.table-package and could not complete this challenge. I think I would be able to do it if I still had more time to understand it.

# Challenge

I used the reduced data since the link for the original data did not work.

```{r}
library(vroom)
library(tidyverse)
library(dplyr)
library(data.table)
```

## **Patent Dominance**

**What US company / corporation has the most patents? List the 10 US companies with the most assigned/granted patents.**

I think I did okay with the first question, but I did not really use the data.table-package. I guess I forgot to actually turn it into a data.table. And I don't know if I even used the right columns. 

````{r}
# Data preparation ----
# Alternative 1:
col_types <- list(    # reduced because the link for the original USPTO data was broken
  id = col_character(),
  #type = col_character(),
  #number = col_character(),
  #country = col_character(),
  date = col_date("%Y-%m-%d"),
  #abstract = col_character(),
  #title = col_character(),
  #kind = col_character(),
  num_claims = col_double()
  #filename = col_character(),
  #withdrawn = col_double()
)

patent_tbl <- vroom(
  file       = "../../Patent_data_reduced/patent.tsv", 
  delim      = "\t", 
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)

# assignee_tbl prep
assignee_col_types <- list(
  id = col_character(),
  type = col_character(),
  organization = col_character()
)

assignee_tbl <- vroom(
  file       = "../../Patent_data_reduced/assignee.tsv", 
  delim      = "\t", 
  col_types  = assignee_col_types,
  na         = c("", "NA", "NULL")
)

# patent_assignee_tbl prep
patent_assignee_col_types <- list(
  patent_id = col_character(),
  assignee_id = col_character()
)

patent_assignee_tbl <- vroom(
  file       = "../../Patent_data_reduced/patent_assignee.tsv", 
  delim      = "\t", 
  col_types  = patent_assignee_col_types,
  na         = c("", "NA", "NULL")
)

# 1. Patent Dominance: What US company / corporation has the most patents? ----
# List the 10 US companies with the most assigned/granted patents.

# Rename id to assignee_id
setnames(assignee_tbl, "id", "assignee_id")

# Combine Data
combined_assignee_tbl <- merge(x = assignee_tbl, y = patent_assignee_tbl,
                               by = "assignee_id",
                               all.x = TRUE, 
                               all.y = FALSE)

setnames(patent_tbl, "id", "patent_id")

combine_patent_assignee_tbl <-  merge(x = combined_assignee_tbl, y = patent_tbl,
                                      by = "patent_id",
                                      all.x = TRUE, 
                                      all.y = FALSE)

combine_patent_assignee_tbl %>%
  group_by(organization) %>%
  summarise(granted_patents = sum(num_claims)) %>%
  ungroup() %>%
  arrange(desc(granted_patents)) %>%
  slice(1:10)
# I couldn't extract US companies
```

## **Recent patent activity**

**What US company had the most patents granted in August 2014? List the top 10 companies with the most new granted patents for August 2014.**

I couldn't finish this one. I did not understand how to set up the command to sort it by the organization, year, and month.

```{r}
# 2. Recent patent activity: What US company had the most patents granted in August 2014? ----
# List the top 10 companies with the most new granted patents for August 2014.

split_date_patent_tbl <- combine_patent_assignee_tbl %>%
  mutate(date = as.character(date))%>%
  separate(col = date,
           into = c("year", "month", "day"),
           sep = "-", remove = TRUE) %>%
  mutate(
    year = as.numeric(year),
    month = as.numeric(month),
    day = as.numeric(day)
  )

split_date_patent_dt <- as.data.table(split_date_patent_tbl)
class(split_date_patent_dt)

split_date_patent_dt %>%
  mutate(num_claims = as.numeric(num_claims)) %>%
  view()

setkey(split_date_patent_dt, "organization")
key(split_date_patent_dt)

setorderv(split_date_patent_dt, c("organization", "year", "month"))

# split_date_patent_dt[, ] # I don't know...
```

## **Innovation in Tech**

**What is the most innovative tech sector? For the top 10 companies (worldwide) with the most patents, what are the top 5 USPTO tech main classes?**

I did not even start this one.
