---
title: "Data Visualization"
author: "Franziska Nissen"
---

# Challenge 1

Unfortunately I was not able to print the y-axis-label in English. I also was not able to use `geom_label()` because I could not figure out how to only label the United States and on the end position. When I set it to a specific position the legend was referring to the text and not the line anymore...

```{r plot, fig.width=10, fig.height=7}
library(tidyverse)
library(RColorBrewer)
library(lubridate)

covid_data_tbl <- read_csv("https://covid.ourworldindata.org/data/owid-covid-data.csv")

# I'll need the following: continent, location, date, total cases

# Data Manipulation

covid_time_tbl <- covid_data_tbl %>%
  select(location, continent, date, total_cases) %>%
  filter(location %in% c("Germany", "United Kingdom", "France", "Spain", "United States")) %>%
  mutate(final_cases = max(total_cases, na.rm = TRUE)) %>% 
  mutate(across(total_cases, ~replace_na(., 0))) 


# Data Visualization

covid_time_tbl %>%
  
  ggplot(aes(date, total_cases, color = location))+
  
  geom_line(linewidth = 1)+
  #geom_label(aes(x = as.Date("2023-05-24"), y = 103436829, 
  #       label = "103.436.829"), show.legend = TRUE)+
  annotate(geom="text", x=as.Date("2023-05-24"), y= 107000000, 
           label="103.436.829") +
  
  # Formatting
  labs(
    title = "COVID-19 confirmed cases",
    subtitle = "as of 24/05/2023",
    y = "Cumulative Cases",
    x = ""
  )+
  scale_y_continuous(breaks = seq(0, 120000000, by = 20000000), minor_breaks = seq(0, 120000000, by = 10000000),
                     labels = scales::label_number(scale = 1e-6, 
                                                    prefix = "",
                                                    suffix =" M"))+
  scale_x_date(date_breaks = "2 months", date_labels = (date_format = "%B '%y"))+
  scale_color_brewer("Countries", palette = "Dark2")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.text.y = element_text(),
    axis.title.y = element_text(face = "bold"),
    axis.title.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_line(color = "grey"),
    panel.background = element_blank()
  )
```





# Challenge 2

This is the best I could do with the time I had. I could not render it and did not have the time to figure out why... It says it cannot use `x = long, y = lat,` so I took out and now there is no visual map. It actually is a map and looks really familiar to the one you uploaded... So I will just give you this.

```{r}
library(maps)
library(tidyverse)
library(RColorBrewer)
library(lubridate)

covid_data_tbl <- read_csv("https://covid.ourworldindata.org/data/owid-covid-data.csv")

world <- map_data("world") %>%
  select(region)

world_map <- map_data("world")

covid_world_tbl <- covid_data_tbl %>%
  select(location, new_deaths, population) %>%
  mutate(across(new_deaths, ~replace_na(., 0))) %>%
  group_by(location, population) %>%
  summarise(deaths = sum(new_deaths)) %>%
  ungroup() %>%
  mutate(mortality = deaths / population) %>%
  mutate(location = case_when(
    location == "United Kingdom" ~ "UK",
    location == "United States" ~ "USA",
    location == "Democratic Republic of Congo" ~ "Democratic Republic of the Congo",
    TRUE ~ location
  )) %>%
  distinct() %>%
  right_join(world, by = c("location" = "region"))

sum(covid_world_tbl$deaths, na.rm = TRUE)
 

# Data Visualization

covid_world_tbl %>%
  
  ggplot(aes( fill = mortality)) +
  geom_map(aes( map_id = location), map = world_map) + 
  
  # formatting
  labs(
    title = "Confirmed COVID-19 deaths relative to the size of the population",
    subtitle = "Around 15.4 Million confirmed COVID-19 deaths worldwide",
    y = "",
    x = ""
  )+
  theme(
    axis.text = element_blank(),
    axis.ticks = element_blank()
  )
```

